---
title: "Audio_Separation_tit"
output: html_document
date: "2025-06-19"
---
Author: Parker Major 

Date: 06/19/2025 Revised: 06/20/2025

Purpose: Conduct interobserver reliability test for call unit annotation. Both annotators labeled the first 25 videos of the set with 4 possible labels ("Tit", "2+Tits", "Speech", "Other"), only Tit and 2+Tits are used for reliability testing. One annotator (S) included an additional label "Silence" which does not effect results.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
#Clear global environment
rm(list = ls())

#Load in required packages
tmp <- c("readtextgrid", "tidyverse", "irr", "irrCAC", "ggplot2")
invisible(lapply(tmp, library, character = TRUE))

```

### Set up usable data frame containing all .TextGrid information from both annotators 
```{r, results="hide"}
#Set path
path <- "/Users/parkermajor/Desktop/Separation_annotations_tit"

#Load in .TextGrid files contained within the folder denoted in path above 
textgrid_files <- list.files(path = path, pattern = "\\.TextGrid$", full.names = TRUE, recursive = TRUE)

#Create function that extracts the folder name (either N or P) within the path folder
get_annotator <- function(file_path) {
  parts <- str_split(file_path, "/")[[1]]
  annotator <- parts[length(parts) - 1]
  return(annotator)
  }

#Add annotator column to .TextGrid data 
textgrids <- map(textgrid_files, function(file) {
  annotator <- get_annotator(file)
  read_textgrid(file) %>%
    mutate(
      file = basename(file),
      annotator = annotator)})

#Create combined data frame with data from both annotators 
combined_data <- bind_rows(textgrids)

#Filter out empty intervals (only keep those that contain a text label), rename columns to be more readable and remove unnecessary columns 
cleaned_data <- combined_data %>% 
  filter(text != "") %>% 
  select(file, start_time = xmin, end_time = xmax, label = text, annotator)

#Round all start and end times to two decimal points 
rounded_data <- cleaned_data %>%
  mutate(
    start_time = round(start_time / 0.01) * 0.01,
    end_time   = round(end_time / 0.01) * 0.01
  )

```

### Conduct interobserver comparison test (Gwet's AC1)
```{r, results="hide"}
#Create function that sets up time points and the corresponding label given by each annotator in each time point
time_point <- function(data, unit) {
  data %>%
    filter(!is.na(start_time), !is.na(end_time)) %>%
    filter(end_time - start_time >= unit) %>% 
    rowwise() %>%
    mutate(time = list(seq(from = start_time, to = end_time - unit, by = unit))) %>%
    unnest(cols = c(time)) %>%
    mutate(time = round(time, 2)) %>%
    select(file, annotator, time, label)
}
#New data frame sorted using function above
comparison <- time_point(rounded_data, unit = 0.01)

#Reorganize comparison data frame to more easily compare annotator labels in a given time point 
comparison <- comparison %>%
  group_by(file, time, annotator) %>%
  slice(1) %>%
  ungroup()

#Filter to only keep time point in which at least 1 annotator had the label "Tit" or "2+Tits" 
tmp_filter <- comparison %>%
  filter(label %in% c("Tit", "2+Tits"))

#Pivot to replace annotator column with two new columns, one for each annotator
comparison_pivot <- tmp_filter %>%
  pivot_wider(names_from = annotator, values_from = label) 

#Rename NA's to "None" 
comparison_pivot[is.na(comparison_pivot)] <- "None"

#Remove file and time columns for ease of analysis 
labels <- comparison_pivot %>% select(-file, -time)

#Run Cohen's kappa 
kappa2(labels, weight = "unweighted")
#Kappa = 0.344, poor agreement, p = 0

labels %>% count(I)
#2+Tits   322 (3.34%)
#None     719 (7.47%)
#Tit     8587 (89.2%)
#Total = 9628

labels %>% count(S)
#2+Tits   485 (5.04%)
#None     432 (4.49%)
#Tit     8711 (90.5%)
#Total = 9628

gwet.ac1.raw(labels)
#AC1 = 0.877, p = 0, CI(0.87, 0.884)
#Almost perfect agreement

```

### Create confusion matrix to display agreement results 
```{r}
conf_mat <- as.data.frame(table(labels[[1]], labels[[2]]))
colnames(conf_mat) <- c("AnnotatorI", "AnnotatorS", "Count")

order <- c("None", "Tit", "2+Tits")
conf_mat$AnnotatorI <- factor(conf_mat$AnnotatorI, levels = order)
conf_mat$AnnotatorS <- factor(conf_mat$AnnotatorS, levels = order)

ggplot(conf_mat, aes(x = AnnotatorI, y = AnnotatorS, fill = sqrt(Count))) +
  geom_tile(color = "white") +
  geom_text(aes(label = Count), color = "black", size = 4) +
  scale_fill_gradient(low = "white", high = "orchid4") +
  labs(x = "Annotator I", y = "Annotator S", fill = "Count") +
  guides(fill = "none") +
  coord_fixed() +
  theme_minimal()  +
  labs(title = "Confusion Matrix (Count)")
```

